---
title: KaggleHelper
author: ~
date: '2018-06-17'
slug: another-new-post
categories: [projects]
tags: [data science]
---

During week 2 of iX data science, Mary Lin and I created a package to aid us in making a good score in the Home Credit Default Risk Kaggle competition.

We created two functions:
 
Our first, replaceNansWithMedian takes two parameters: a dataframe, and the name of the column you'd like to modify and returns a new dataframe that has a newly median imputed colum in place of the old.  

Below is the code for replaceNansWithMedian. 
```{r}

library(devtools)
library(roxygen2)

replaceNansWithMedian <- function(df, colName) {
  colMedian <- median(df[[colName]], na.rm=TRUE)
  df[[colName]] <- tidyr::replace_na(df[[colName]], colMedian)
  return(df)
}
```


Second, we created writeCSV, which takes in your test data, your predictions, and a desired .csv filename.  The function simply takes in these parameters, converts data into a dataframe, and writes that dataframe to a new .csv vbased on your inputted filename.

Here's the code for writeCSV.
```{r}
library(devtools)
library(roxygen2)

writeCSV <- function(testdata, predictstatement, filename="yourAnswer") {
  fit2 <- data.frame(SK_ID_CURR = testdata$SK_ID_CURR, TARGET = predictstatement)
  write.csv(fit2, filename, row.names = FALSE, col.names = FALSE)
}
```


Overall, replaceNansWithMedian was inifinitely more useful than writeCSV.  Using an easy for loop, imputing median values into our data was made easy by KaggleHelper.
